---
title: "MS 4 - Data Collection Overview"
author: "Arushi Saxena"
date: "3/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#install.packages("rtweet")
library(rtweet)
```
### Data Source 1: Russian Troll Tweets from FiveThirtyEight
<b>Goal </b>: Main data source for exploration. 

* Potential charts I am looking into include:
  + Do a word cloud on their common themes 
  + Pick top 5 themes from word cloud to explore further  
  + For each of the 5 themes, do a comparative distribution over time. This will help us understand - are the trolls talking about same things at same time? Or do the talk about similar topics earlier or later than the other? Is there coordination between accounts?
  + Sentiment Analysis of the tweets. Do Russian trolls use positive propaganda or negative propaganda? How does this differ for each of the 5 themes?
  + A geographic map of which states / countries the trolls discuss most. How does this map change by month? How does it track versus geographies discussed tweets from major US news handles?
  
<b>Current Status</b>: There is a set of approximately 60 CSV files I have downloaded. I have learnt how to convert them to RDS to read and process them more efficiently but I am trying to assess if there is anyway to combine all 60 CSVs (or multiple CSVs into one single RDS file). I am currently doing this research via Github and believe I had found a way: https://stackoverflow.com/questions/56020249/using-r-to-merge-many-large-csv-files-across-sub-directories

<b>Next Steps</b>:
1. Convert all CSVs into RDS
2. Begin data cleaning and word cloud analysis

```{r}
# Read and save this example file locally
# a <- read.csv(file="https://raw.githubusercontent.com/fivethirtyeight/russian-troll-tweets/master/IRAhandle_tweets_1.csv") 
```

```{r making the RDS}
# saveRDS(a, file ="RussianTweets.RDS")
# RussianTweets <- readRDS("RussianTweets.RDS")
```

### Data Source 2: 2016 Tweets from Reuters Twitter handle
<b>Goal</b>: Compare the content from Reuters Twitter handle to Russian troll tweets to see how topical the IRA tweets are and to assess time lag between certain discussion topics. I have currently narrowed in on Reuters since it is acknowledged 
<b> Next Steps </b>: Once my Twitter Developer Access request is approved, I will follow these steps here to get a Twitter token: https://rtweet.info/articles/auth.html 

```{r getting Twitter token}

```


```{r}
#This is example from https://community.rstudio.com/t/how-to-collecting-twitter-data-from-past-year/22568/3 

# tweets <- get_timelines("hadleywickham", 
#                         n = 10000, 
#                         language = 'en',
#                         since = '2014-01-01', 
#                         until = '2014-12-31')
#                         #token = twitter_token
```

